### 2022-09-27 main/chapter_context.tex
clean up some bib names

\subsection{The Standard Model}
\label{sec:context_sm}
\TODO{particle content figure/tables}

The current Standard Model features three generations of fermions,
which interact through forces mediated by vector bosons
and the scalar Higgs boson.
The strong force is mediated by
Massless gluons $g$ mediate the strong force,
the massless photon $\gamma$ mediates the electromagnetic force,
and very massive $W^+$, $W^-$, and $Z$ bosons weadiate the weak force.

>>>>

\subsection{The Standard Model}
\label{sec:context_sm}
The current Standard Model features three generations of fermions,
which interact through forces mediated by vector bosons
and the scalar Higgs boson.
The strong force is mediated by
Massless gluons $g$ mediate the strong force,
the massless photon $\gamma$ mediates the electromagnetic force,
and very massive $W^+$, $W^-$, and $Z$ bosons weadiate the weak force.
\TODO{particle content figure/tables}
